---
title: "Twitch Streamer Presentation"
author: "CARLS <br> Craig, Adi, Ronan, Lauren, and Sophia"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(ggplot2)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Load your data here
twitchdata <- read.csv("twitchdata-update.csv")
```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/confetti.jpg"
)
```

class: center, middle

## How stream time affects watch time and followers gained.

---

class: inverse, center, middle

# Introduction

---

# Research Question and Data

- How does stream time affect watch time and followers gained?

- This data was found through Awesome Public Datasets and was downloaded from Kaggle.com .

- There are `r nrow(twitchdata)` different entries and `r ncol(twitchdata)` different variables.


---

class: inverse, middle, center

# Analysis Plan

---

# Important Variables

- Channel, Nominal Categorical Variable 

- Stream Time, Discrete Numerical Variable

- Watch Time, Discrete Numerical Variable 

- Followers Gained, Discrete Numerical Variable

--


---

# Comparisons

You can use plain text

- or bullet points

.pull-left[
or text in two columns $^*$
]
.pull-right[
- like
- this
]

.footnote[
[*] And add footnotes
]

---

# Prelim data analysis (stats etc.)

.pull-left[
- Some languages are more popular, language may have an effect on the number of views
- May need to try averages per language, or try to summerise data for followers gained (maybe as a percentage)
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(twitchdata, 
       aes(y = Language,
           fill = Language)) +
  geom_bar() +
  theme_minimal()
```
]
---

# Important Stats

```{r recode-species, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
language_data <- count(twitchdata, Language, sort= TRUE)
print(language_data)
```
---
```{r plot-data, echo = FALSE, warning=FALSE}
# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the look
ggplot(data = twitchdata, 
       mapping = aes(x = Stream.time.minutes., 
                     y = Followers.gained,
                     color=Language)) +
                 geom_point() + 
                 labs (title = "Stream Time to Followers Gained",
                       subtitle = "",
                       x = "Stream Time (min)",
                       y = "Followers Gained") +
                 theme_minimal() # theme options: https://ggplot2.tidyverse.org/reference/ggtheme.html
```

---

## Results needed to support hypothesis

.pull-left[
- Some text
- goes here
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
```
]

---

# Images

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

Or you can also include a full page image. See next slide.

---

background-image: url(https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80)

---



# Feeling adventurous?

- Want to find out more about `xaringan`? See https://slides.yihui.name/xaringan/#1.

- You are welcomed to use the default styling of the slides. In fact, that's what I expect majority of you will do. You will differentiate yourself with the content of your presentation.

- But some of you might want to play around with slide styling. The 
`xaringanthemer` provides some solutions for this that: https://pkg.garrickadenbuie.com/xaringanthemer.

- And if you want more bells and whistles, there is also `xaringanExtra`: https://pkg.garrickadenbuie.com/xaringanExtra.
