--
title: "Twitch Streamer Report"
author: "CARLS <br> Craig, Adi, Ronan, Lauren, and Sophia"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(ggplot2)
library(tidymodels)
```

----

## Twitch Streamer Report

### Our Data 

_We started off by picking the twitch streamers dataset which we got through Awesome Public Datasets and downloaded from Kaggle. We decided to go with this dataset as we thought it would be very interesting to look at data from a recently introduced platform that has not been studied in excessive detail._


```{r load_data}
twitchdata <- read.csv("twitchdata-update.csv")
```

----
## What is Twitch?

_Twitch is an American company with a particular focus on gaming and live streaming content.A twitch streamer is someone who uses the platform Twitch to livestream content to others across the world._


## Hypothesis

_Our initial hypothesis was to identify the correlation between stream time and watch time as well as followers gained. To do so we started off by compiling a list of the primary language used by the streamers and the frequency of them. This was then put into a table and we discovered that the number of people who spoke each language ranged from 1 to 485, with English being the widest spoken language at 485. While this is interesting English is the most widely spoken with the next one down being Korean at 77. This would make language comparisons difficult as English dominates the data greatly and thus English would be over represented in analysis linked to language. This prompted our decision to focus mainly on streamers who spoke English._


```{r warning=FALSE, out.width="30%", fig.width=4, echo=FALSE}
ggplot(twitchdata, 
       aes(y = Language,
           fill = Language)) +
  geom_bar() +
  theme_minimal()

```


## Data Wrangling 
_After this we made a graph of stream time verses followers gained. We then filtered them by language. However there didn’t appear to be any correlation. After this we were advised by our tutor to look at the log and square of the data and see if that produced a correlation, when that still didn’t show any strong correlation we decided to change our question slightly. To look at how follower numbers and followers gained are affected by various variables, namely Stream time and watch time._
 

_When our data still did not show a correlation we decided to augment it by taking the log of our data and did our graphs using this:_

```{r twitchdata, warning = FALSE}
twitchdata <- mutate(twitchdata,
                     Gain.percent = 100*Followers.gained/(Followers-Followers.gained),
                     log_Watch.time.Minutes. = log(Watch.time.Minutes.),
                     log_Followers = log(Followers),
                     log_Stream.time.minutes. = log(Stream.time.minutes.),
                     log_Average.viewers = log(Average.viewers))
language_data <- count(twitchdata, Language, sort= TRUE)
```



## Plots and Graphs

_In the following graphs, we only accounted for English-speaking streamers, and took the natural log of each variable.  The graphs below represent the correlations between different variables of this data set, and can be used to predict the relationships that exist between them;_

_In this graph, we compared the values for Stream Time (the amount of time an individual streams on Twitch, in minutes) with the values for Watch Time (the amount of time spent by viewers watching the stream, in minutes).  Between 11 and 12 minutes of stream time, there is a cluster of points, which may be a result of overrepresentation of individuals that stream for this amount of time._

```{r StreamTime_WatchTime, echo=FALSE}
twitchdata %>%
  filter(Language == "English") %>%
  ggplot(mapping = aes(x = log(Stream.time.minutes.), 
                       y = log(Watch.time.Minutes.))) +
                 geom_point() + 
                 labs (title = "Stream Time to Watch time",
                       x = "ln Stream Time (min)",
                       y = "ln Watch Time (min)") +
          geom_smooth()
```


_This graph displays the relationship between Watch Time and Followers (the number of people following the streamer).  We took the log of the values for the Watch Time variable, with the values for the Followers variable remaining the same.  There is a slight linear relationship between these variables, indicating that a higher watch time suggests a higher number of followers.  However, this correlation is not sufficient to definitively establish this relationship between Watch Time and Followers._
``` {r WatchTime_Followers, echo = FALSE}
twitchdata %>%
  filter(Language == "English") %>%
  ggplot(mapping = aes(x = log(Watch.time.Minutes.), 
                       y = log(Followers))) +
                 geom_point() + 
                 labs (title = "Watch Time to Followers",
                       x = "ln Watch Time (min)",
                       y = "Followers") +
        geom_smooth(method = "lm")
```

_This graph displays the relationship between a streamer’s watch time and the percent change in their amount of followers (Followers Gained).  We filtered out data where the percentage of followers gained was an outlier (such as data points where a streamer suddenly gained an abnormally large amount of followers at once, which would have altered the validity of the relationship between variables).  Similar to the graph above, Watch Time was taken as a natural log, with Followers Gained taken as a percentage. _
``` {r WatchTime_PercentageGain, echo = FALSE}
twitchdata %>%
  filter(Language == "English") %>%
 filter(Gain.percent < quantile(Gain.percent, 0.9) &
        Gain.percent > quantile(Gain.percent, 0.1)) %>%
  ggplot(mapping = aes(x = log(Watch.time.Minutes.), 
                       y = (Gain.percent))) +
                 geom_point() + 
                 labs (title = "Watch Time to Followers Gained",
                       x = "ln Watch Time (min)",
                       y = "Followers Gained (%)") +
        geom_smooth()
```

_This graph examines the relationship between the amount of time streamed and the total number of followers the streamer has.  In this graph we took the natural log of both the Stream Time variable and the Followers variable.  This graph shows a clear linear relationship between these variables, in which higher stream time can be associated with a higher follower count.  There is also a large cluster of data points between 8 and 10 minutes of stream time._
``` {r StreamTime_Followers, echo = FALSE}
twitchdata %>%
  filter(Language == "English") %>%
  ggplot(mapping = aes(x = log(Peak.viewers), 
                       y = log(Average.viewers))) +
                 geom_point() + 
                 labs (title = "Stream Time to Followers",
                       x = "ln Stream Time (min)",
                       y = "ln Followers") +
        geom_smooth()
```

_This graph compares the amount of stream time with the average number of viewers watching the stream (represented by the Viewers variable), with the natural log taken of each variable.  There is a large cluster of points between 11 and 12 minutes of stream time.  There is a linear relationship that shows a shorter stream time being associated with a higher average number of viewers , and longer stream time with less average viewers._
``` {r StreamTime_AverageViews, echo = FALSE}
twitchdata %>%
  filter(Language == "English") %>%
  ggplot(mapping = aes(x = log(Stream.time.minutes.), 
                       y = log(Average.viewers))) +
                 geom_point() + 
                 labs (title = "Stream Time to Average Viewers",
                       x = "ln Stream Time (min)",
                       y = "ln Viewers") +
        geom_smooth()
```
_How total followers affect number of viewers. Again only english streamers. log taken of both sides._
``` {r Followers_Viewers, echo = FALSE}
twitchdata %>%
  filter(Language == "English") %>%
  ggplot(mapping = aes(x = log(Followers), 
                       y = log(Average.viewers))) +
                 geom_point() + 
                 labs (title = "Average Viewers to Followers",
                       x = "ln Followers ",
                       y = "ln Average Viewers") +
        geom_smooth()
```

_How Watch time affect number of viewers. Again only english streamers. Natural log taken of both sides._
``` {r StreamTime_PercentageGain, echo = FALSE}
twitchdata %>%
  filter(Language == "English") %>%
  ggplot(mapping = aes(x = log(Watch.time.Minutes.), 
                       y = log(Average.viewers))) +
                 geom_point() + 
                 labs (title = "Watch time to Average Viewers",
                       x = "ln Watch time (min) ",
                       y = "ln Average Viewers") +
        geom_smooth()
```

## Models

_Anything with a 1 after it is part of the model for ln watch time by using ln stream time and ln followers. Anything with a 2 after it is for a model that predicts viewers based on followers, watch time and stream time. All models only work for english streamers. The first model has an r squared of 0.42, and the second has an r squared of 0.98._

```{r split-data}
englishdata <- filter(twitchdata, Language == "English")
set.seed(1234)
twitchdata_split <- initial_split(englishdata)
twitchdata_train <- training(twitchdata_split)
twitchdata_test  <- testing(twitchdata_split)
```

```{r recipe}
twitchdata_recipe_1 <- recipe(log_Watch.time.Minutes. ~ log_Followers +
                                log_Stream.time.minutes.,
                      data = englishdata)
twitchdata_recipe_2 <- recipe(log_Average.viewers ~ log_Followers +
                                log_Watch.time.Minutes. +
                                log_Stream.time.minutes.,
                              data = englishdata)
```

```{r model}
twitchdata_spec_1 <- linear_reg() %>%
  set_engine("lm")
twitchdata_spec_2 <- linear_reg() %>%
  set_engine("lm")
```

```{r workflow}
twitchdata_wflow_1 <- workflow() %>%
  add_model(twitchdata_spec_1) %>%
  add_recipe(twitchdata_recipe_1)

twitchdata_wflow_2 <- workflow() %>%
  add_model(twitchdata_spec_2) %>%
  add_recipe(twitchdata_recipe_2)
```

```{r fit}
twitchdata_fit_1 <- twitchdata_wflow_1 %>%
  fit(data = twitchdata_train)
tidy(twitchdata_fit_1)

twitchdata_fit_2 <- twitchdata_wflow_2 %>%
  fit(data = twitchdata_train)
tidy(twitchdata_fit_2)
```

```{r pred}
twitchdata_pred_1 <- predict(twitchdata_fit_1, 
                             twitchdata_test) %>%
  bind_cols(twitchdata_test)

twitchdata_pred_2 <- predict(twitchdata_fit_2, 
                             twitchdata_test) %>%
  bind_cols(twitchdata_test)
```

```{r accuracy}
glance(twitchdata_fit_1)$adj.r.squared
glance(twitchdata_fit_2)$adj.r.squared
```

