--
title: "Twitch Streamer Report"
author: "CARLS <br> Craig, Adi, Ronan, Lauren, and Sophia"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(ggplot2)
library(tidymodels)
```

----

## Twitch Streamer Report

### Our Data 

_We started off by picking the twitch streamers dataset which we got through Awesome Public Datasets and downloaded from Kaggle. We decided to go with this dataset as we thought it would be very interesting to look at data from a recently introduced platform that has not been studied in excessive detail._


```{r load_data}
twitchdata <- read.csv("twitchdata-update.csv")
```

----
## What is Twitch?

_Twitch is an American company with a particular focus on gaming and live streaming content.A twitch streamer is someone who uses the platform Twitch to livestream content to others across the world._


## Hypothesis

_Our initial hypothesis was to identify the correlation between stream time and watch time as well as followers gained. To do so we started off by compiling a list of the primary language used by the streamers and the frequency of them. This was then put into a table and we discovered that the number of people who spoke each language ranged from 1 to 485, with English being the widest spoken language at 485. While this is interesting English is the most widely spoken with the next one down being Korean at 77. This would make language comparisons difficult as English dominates the data greatly and thus English would be over represented in analysis linked to language. This prompted our decision to focus mainly on streamers who spoke English._


## Data Wrangling 
_After this we made a graph of stream time verses followers gained. We then filtered them by language. However there didn’t appear to be any correlation. After this we were advised by our tutor to look at the log and square of the data and see if that produced a correlation, when that still didn’t show any strong correlation we decided to change our question slightly. To look at how follower numbers and followers gained are affected by various variables, namely Stream time and watch time._
 

_When our data still did not show a correlation we decided to augment it by taking the log of our data and did our graphs using this:_

```{r twitchdata, warning = FALSE}
twitchdata <- mutate(twitchdata,
                     Gain.percent = 100*Followers.gained/(Followers-Followers.gained),
                     log_Watch.time.Minutes. = log(Watch.time.Minutes.),
                     log_Followers = log(Followers),
                     log_Stream.time.minutes. = log(Stream.time.minutes.),
                     log_Average.viewers = log(Average.viewers))
language_data <- count(twitchdata, Language, sort= TRUE)
```



## Plots and Graphs

_Stream Time to Watch Time, considering only English streamers. Natural log taken of both sides_
```{r StreamTime_WatchTime, echo=FALSE}
twitchdata %>%
  filter(Language == "English") %>%
  ggplot(mapping = aes(x = log(Stream.time.minutes.), 
                       y = log(Watch.time.Minutes.))) +
                 geom_point() + 
                 labs (title = "Stream Time to Watch time",
                       x = "ln Stream Time (min)",
                       y = "ln Watch Time (min)") +
          geom_smooth()
```


_How watch time affects followers (total). Again using only english streamers. Taking the natural log of both variables _
``` {r WatchTime_Followers, echo = FALSE}
twitchdata %>%
  filter(Language == "English") %>%
  ggplot(mapping = aes(x = log(Watch.time.Minutes.), 
                       y = log(Followers))) +
                 geom_point() + 
                 labs (title = "Watch Time to Followers",
                       x = "ln Watch Time (min)",
                       y = "Followers") +
        geom_smooth(method = "lm")
```

_How watch time affects followers gained (total). Again only english streamers. Filtered out data where percentage gained is an outlier (and morphs the scale). Watch time is taken as the natural log. _
``` {r WatchTime_PercentageGain, echo = FALSE}
twitchdata %>%
  filter(Language == "English") %>%
 filter(Gain.percent < quantile(Gain.percent, 0.9) &
        Gain.percent > quantile(Gain.percent, 0.1)) %>%
  ggplot(mapping = aes(x = log(Watch.time.Minutes.), 
                       y = (Gain.percent))) +
                 geom_point() + 
                 labs (title = "Watch Time to Followers",
                       x = "ln Watch Time (min)",
                       y = "Followers Gained (%)") +
        geom_smooth()
```

_How Stream time affects followers (total). Again only english streamers. Natural log is taken of both variables._
``` {r StreamTime_Followers, echo = FALSE}
twitchdata %>%
  filter(Language == "English") %>%
  ggplot(mapping = aes(x = log(Peak.viewers), 
                       y = log(Average.viewers))) +
                 geom_point() + 
                 labs (title = "Stream Time to Followers",
                       x = "ln Stream Time (min)",
                       y = "ln Followers") +
        geom_smooth()
```

_How Stream time affects average viewers. Again only english streamers. Natural log is taken of both variables._
``` {r StreamTime_AverageViews, echo = FALSE}
twitchdata %>%
  filter(Language == "English") %>%
  ggplot(mapping = aes(x = log(Stream.time.minutes.), 
                       y = log(Average.viewers))) +
                 geom_point() + 
                 labs (title = "Stream Time to Average Viewers",
                       x = "ln Stream Time (min)",
                       y = "ln Viewers") +
        geom_smooth()
```
_How total followers affect number of viewers. Again only english streamers. log taken of both sides._
``` {r Followers_Viewers, echo = FALSE}
twitchdata %>%
  filter(Language == "English") %>%
  ggplot(mapping = aes(x = log(Followers), 
                       y = log(Average.viewers))) +
                 geom_point() + 
                 labs (title = "Average Viewers to Followers",
                       x = "ln Followers ",
                       y = "ln Average Viewers") +
        geom_smooth()
```

_How Watch time affect number of viewers. Again only english streamers. Natural log taken of both sides._
``` {r StreamTime_PercentageGain, echo = FALSE}
twitchdata %>%
  filter(Language == "English") %>%
  ggplot(mapping = aes(x = log(Watch.time.Minutes.), 
                       y = log(Average.viewers))) +
                 geom_point() + 
                 labs (title = "Watch time to Average Viewers",
                       x = "ln Watch time (min) ",
                       y = "ln Average Viewers") +
        geom_smooth()
```

## Models

_Anything with a 1 after it is part of the model for ln watch time by using ln stream time and ln followers. Anything with a 2 after it is for a model that predicts viewers based on followers, watch time and stream time. All models only work for english streamers. The first model has an r squared of 0.42, and the second has an r squared of 0.98._

```{r split-data}
englishdata <- filter(twitchdata, Language == "English")
set.seed(1234)
twitchdata_split <- initial_split(englishdata)
twitchdata_train <- training(twitchdata_split)
twitchdata_test  <- testing(twitchdata_split)
```

```{r recipe}
twitchdata_recipe_1 <- recipe(log_Watch.time.Minutes. ~ log_Followers +
                                log_Stream.time.minutes.,
                      data = englishdata)
twitchdata_recipe_2 <- recipe(log_Average.viewers ~ log_Followers +
                                log_Watch.time.Minutes. +
                                log_Stream.time.minutes.,
                              data = englishdata)
```

```{r model}
twitchdata_spec_1 <- linear_reg() %>%
  set_engine("lm")
twitchdata_spec_2 <- linear_reg() %>%
  set_engine("lm")
```

```{r workflow}
twitchdata_wflow_1 <- workflow() %>%
  add_model(twitchdata_spec_1) %>%
  add_recipe(twitchdata_recipe_1)

twitchdata_wflow_2 <- workflow() %>%
  add_model(twitchdata_spec_2) %>%
  add_recipe(twitchdata_recipe_2)
```

```{r fit}
twitchdata_fit_1 <- twitchdata_wflow_1 %>%
  fit(data = twitchdata_train)
tidy(twitchdata_fit_1)

twitchdata_fit_2 <- twitchdata_wflow_2 %>%
  fit(data = twitchdata_train)
tidy(twitchdata_fit_2)
```

```{r pred}
twitchdata_pred_1 <- predict(twitchdata_fit_1, 
                             twitchdata_test) %>%
  bind_cols(twitchdata_test)

twitchdata_pred_2 <- predict(twitchdata_fit_2, 
                             twitchdata_test) %>%
  bind_cols(twitchdata_test)
```

```{r accuracy}
glance(twitchdata_fit_1)$adj.r.squared
glance(twitchdata_fit_2)$adj.r.squared
```